### 2021-12-02 cn/abstracts.tex
Add files via upload

\section*{会议摘要}

\begin{etaremune}
\item Wei, S. S., Shearer, P. M., Lithgow-Bertelloni, C., Stixrude, L., \& \Tian\ (2021).
	Oceanic plateau of the Hawaiian mantle plume head subducted to the uppermost lower mantle,
	Abstract EGU21-13874 virtually presented at EGU General Assembly 2021.
\item \Tian, Wang, W., Wang, F., \& Wei, S. S. (2020).
	Source spectra of intermediate-depth and deep earthquakes in the Tonga subduction zone.
	Abstract S054-0012 virtually presented at 2020 AGU Fall Meeting.
\item Wei, S. S., \Tian, Shearer, P. M., Lv, M., Dorfman S. M., Lithgow-Bertelloni, C. R., \& Stixrude, L. P. (2020).
	Compositional heterogeneities in the mid-mantle revealed by seismic discontinuities and reflectors.
	Abstract DI016-0008 virtuablly presented at 2020 AGU Fall Meeting.
\item \Tian, Wang, W. \& Wei, S. S. (2019).
	Source spectra and stress drop of deep earthquakes in the Tonga subduction zone.
	Abstract S13C-0458 presented at 2019 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Tian, Wei, S. S., \& Shearer, M. P. (2019).
    Global variations of the 520-km discontinuity.
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Tian, Wei, S. S., \& Shearer, M. P. (2018).
    Global variations of the 520-km discontinuity.
    Abstract DI31C-0024 presented at 2018 AGU Fall Meeting, Washington, DC, USA.
\item
    \Tian, Yao, J., \& Wen, L. (2017).
    Collapse and earthquake swarm after North Korea's 3 September 2017 nuclear test.
    Abstract S43H-2968 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \Tian, \& Wen, L. (2017).
    Three types of Earth's inner core boundary.
    Abstract DI33B-0404 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    Yao, J., \Tian, \& Wen, L. (2017).
    High-precision location, yield and tectonic release of North Korea's 3 September 2017 nuclear test.
    Abstract S43H-2967 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    Yao, J., \Tian, Sun, L., \& Wen, L. (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    Abstract DI33B-0405 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \Tian, \& Wen, L. (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    Yao, J., \Tian, Sun, L., \& Wen, L. (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Tian, \& Wen, L. (2016).
    Seismic structures of the Earth's inner core boundary beneath the Bearing sea and Mexico.
    Abstract DI43A-2657 presented at 2016 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Tian, \& Wen, L. (2015).
    Varying seismic property of the Earth's inner core boundary.
    Abstract DI33A-2606 presented at 2015 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Tian, \& Wen, L. (2014).
    Seismic study on the properties of the Earth's inner core boundary.
    Abstract DI31B-4269 presented at 2014 AGU Fall Meeting, San Francisco, CA, USA.
\item
    Chen, X., \Tian, \& Wen, L. (2013).
    Seismic tracking of hurricane sandy.
    Abstract S11A-2296 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Tian, \& Wen, L. (2013).
    Regional topography variation of Earth's inner core boundary.
    Abstract DI23A-2282 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    Zhang, M., \Tian, \& Wen, L. (2013).
    A new method for earthquake determination: stacking multiple-station autocorrelograms.
    Abstract S51A-2301 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Tian, \& Wen, L. (2012).
    Simulating wave propagation in a faulted medium using a 3D finite difference method.
    Abstract S43A-2458 presented at 2012 AGU Fall Meeting, San Francisco, CA, USA.
\end{etaremune}

### 2021-12-02 cn/activities.tex
Add files via upload

\section*{学术社团及服务}

\begin{itemize}
\item 美国地球物理联合会（AGU）会员（2012至今）
\item 期刊审稿人: \textit{Geophysical Research Letters},
				  \textit{Seismological Research Letters},
				  \textit{Review of Scientific Instruments},
				  \textit{Journal of Open Source Software},
				  \textit{Results in Geophysical Sciences}
\item 创办博客及网站
	  \href{https://blog.seisman.info}{SeisMan 博客} （2013）、
	  \href{http://gmt-china.org/}{GMT 中文社区} （2016）、
	  \href{https://seismo-learn.org/}{地震``学''} （2020）
\item \href{https://github.com/GenericMappingTools/gmt}{Generic Mapping Tools (GMT)} 和 \href{https://github.com/GenericMappingTools/pygmt}{PyGMT} 核心开发者 （2018至今）
\item \href{http://chinageorefmodel.org/}{中国地震学参考模型} 研究助理及数据库管理员 （2016 -- 2018）
\item AGU 秋季会议 Outstanding Student Paper Award 评审（2018 -- 2020）
\item UNAVCO 短期课程 ``The Generic Mapping Tools for Geodesy'' 指导讲师（2019 -- 2021）
\item AGU 秋季会议研讨会 SCIWS4: \href{https://www.agu.org/Events/SCIWS4-Generic-Mapping-Tools}{``Become a Generic Mapping Tools Contributor Even If You Can't Code''} 指导讲师 （2019）
\end{itemize}

### 2021-12-02 cn/publications.tex
Add files via upload

% AGU style: https://publications.agu.org/agu-grammar-and-style-guide/
\newcommand{\Revision}{\textit{正在审稿}}
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author

\section*{已发表论文}
\CS 通讯作者，\CF 共同一作

\begin{etaremune}
\item Yao, J., \Tian, Sun, L., \& Wen, L. (2021).
	Comment on ``Origin of temporal changes of inner-core seismic waves'' by Yang and Song (2020).
	\textit{Earth and Planetary Science Letters}, \textit{553}, 116640.
	\DOI{10.1016/j.epsl.2020.116640}
\item Wei, S. S., Shearer, P. M., Lithgow-Bertelloni, C., Stixrude, L., \& \Tian\ (2020).
	Oceanic plateau of the Hawaiian mantle plume head subducted to the uppermost lower mantle.
	\textit{Science}, \textit{370}, 983--987.
	\DOI{10.1126/science.abd0312}
\item \Tian\CS, Lv, M., Wei, S. S., Dorfman, S. M. \& Shearer, P. M. (2020).
	Global variations of Earth's 520- and 560-km discontinuities.
	\textit{Earth and Planetary Science Letters}, \textit{552}, 116600. \\
	\DOI{10.1016/j.epsl.2020.116600}
\item
    Wessel, P., Luis, J., Uieda, L., Scharroo, R., Wobbe, F., Smith, W. H. F., \& \Tian\ (2019).
    The Generic Mapping Tools Version 6.
    \textit{Geochemistry, Geophysics, Geosystems}, \textit{20}(11), 5556--5564.
    \DOI{10.1029/2019GC008515}
\item
    Yao, J., \Tian, Sun, L., \& Wen, L. (2019).
    Temporal change of seismic Earth's inner core phases: inner core differential rotation or temporal change of inner core surface?.
    \textit{Journal of Geophysical Research: Solid Earth}, \textit{124}(7), 6720--6736.
    \DOI{10.1029/2019JB017532}
\item
    Fan, W., Wei, S.S.,\Tian, McGuire J.J., \& Wiens D.A. (2019).
    Complex and diverse rupture processes of the 2018 Mw 8.2 and Mw 7.9 Tonga-Fiji deep earthquakes.
    \textit{Geophysical Research Letters}, \textit{46}(5), 2434--2448.
    \DOI{10.1029/2018GL080997}
\item
    Yao, J., \Tian\CF, Lu, Z., Sun, L., \& Wen, L. (2018).
    Triggered seismicity after North Korea's 3 September 2017 nuclear test.
    \textit{Seismological Research Letters}, \textit{89}(6), 2085--2093.
    \DOI{10.1785/0220180135}
\item
    Yao, J., \Tian\CF, Sun, L., \& Wen, L. (2018).
	Source characteristics of North Korea's 3 September 2017 nuclear test.
    \textit{Seismological Research Letters}, \textit{89}(6), 2078--2084.
    \DOI{10.1785/0220180134}
\item
    \Tian\CS, Yao, J., \& Wen, L. (2018).
    Collapse and earthquake swarm after North Korea's 3 September 2017 nuclear test.
    \textit{Geophysical Research Letters}, \textit{45}(9), 3976--3983.
    \DOI{10.1029/2018GL077649}
\item
    Wen, L., \Tian, \& Yao, J. (2018).
    Seismic structure and dynamic process of the Earth's inner core and its boundary.
    \textit{Chinese Journal of Geophysics}, \textit{61}(3), 803--818.
    \DOI{10.6038/cjg2018L0500} [in Chinese]
\item
    \Tian, \& Wen, L. (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    \textit{Nature communications}, 8, 165.
    \DOI{10.1038/s41467-017-00229-9}
\item
    Chen, X., \Tian, \& Wen, L. (2015).
    Microseismic sources during hurricane sandy.
    \textit{Journal of Geophysical Research: Solid Earth}, \textit{120}(9), 6386--6403.
    \DOI{10.1002/2015JB012282}
\item Zhang, M., \Tian, \& Wen, L. (2014).
    A new method for earthquake depth determination: stacking multiple-station autocorrelograms.
    \textit{Geophysical Journal International}, \textit{197}(2), 1107--1116.
    \DOI{10.1093/gji/ggu044}
\end{etaremune}

%\subsection*{尚未发表论文（审稿中/修改中）}
%\begin{etaremune}
%\end{etaremune}

### 2021-12-02 en/activities.tex
Add files via upload

\section*{Professional Societies \& Activities}

\begin{itemize}
\item Member of the \href{https://sites.agu.org/}{American Geophysical Union (AGU)} (2012 -- present)
\item Peer-reviewer of scientific journals:
      \textit{Geophysical Research Letters},
      \textit{Seismological Research Letters},
      \textit{Review of Scientific Instruments},
      \textit{Journal of Open Source Software},
      \textit{Results in Geophysical Sciences}
\item Founder of the \href{https://blog.seisman.info}{SeisMan blog} (since 2013),
      \href{http://gmt-china.org/}{GMT China Community} (since 2016)
      and \href{https://seismo-learn.org/}{seismo-learn} (since 2020)
\item Core developer of the \href{https://github.com/GenericMappingTools/gmt}{Generic Mapping Tools (GMT)} and \href{https://github.com/GenericMappingTools/pygmt}{PyGMT} (2018 -- present)
\item Research assistant and database manager for \href{http://chinageorefmodel.org/}{China Seismological Reference Model} (2016 -- 2018)
\item Judge for the Outstanding Student Paper Award, AGU Fall Meeting (2018 -- 2020)
\item Instructor, the UNAVCO Short Course ``The Generic Mapping Tools for Geodesy'' (2019 -- 2021)
\item Instructor, Workshop SCIWS4: \href{https://www.agu.org/Events/SCIWS4-Generic-Mapping-Tools}{``Become a Generic Mapping Tools Contributor Even If You Can't Code''}, 2019 AGU Fall Meeting (2019)
\end{itemize}

### 2021-12-02 en/awards.tex
Add files via upload

\section*{Awards \& Honors}

\begin{tabular}{p{0.05\textwidth} p{0.95\textwidth}}
2021 & One Hundred Talents Program, China University of Geosciences, China \\
2018 & President Award, Chinese Academy of Science, China [\textit{top 1\%}] \\
2018 & Outstanding Graduate Student, University of Science and Technology of China, China [\textit{top 15\%}] \\
2017 & Outstanding Student Paper Award, 2017 Annual Meeting of Chinese Geoscience Union, China \\
2017 & National Scholarship for Doctoral Students, Ministry of Education, China [\textit{top 5\%}] \\
2014 & Kwang-Hua Scholarship, Kwang-Hua Education Foundation, China \\
2010 & Kwang-Hua Scholarship, Kwang-Hua Education Foundation, China \\
2009 & Outstanding Volunteer, University of Science and Technology of China, China \\
\end{tabular}

### 2021-12-02 en/talks.tex
Add files via upload

\section*{Talks}

\begin{etaremune}
\item
	Tectonic-Geophysics Young Scholars Research Symposium.
	Nanjing University.
	Jan. 7, 2021.
\item
	Department of Earth and Space Sciences, Southern University of Science and Techbology.
	Nov. 27, 2020.
	\invited.
\item
    2nd Annual Earth and Environmental Sciences Student Research Symposium.
    Department of Earth and Environmental Sciences, Michigan State University.
    Feb. 23, 2019.
\item
    Institute of Geology and Geophysics, Chinese Academy of Sciences.
    Jun. 15, 2018.
    \invited
\item
    Institute of Earthquake Forcasting, China Earthquake Administration.
    Jun. 14, 2018.
\item
    2017 Annual Meeting of Chinese Geoscience Union (CGU).
    Oct. 17, 2017.
    \invited
\item
    Workshop on Analysis and Applications of Crustal Deformation Data.
    Hubei Earthquake Administration.
    Sep. 21, 2016.
    \invited
\item
    China Earthquake Networks Center.
    Jun. 30, 2016.
    \invited
\end{etaremune}

### 2021-12-02 manuscript.tex
Add files via upload

\documentclass[twocolumn]{article}

\newcommand{\Title}{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}
\newcommand{\Journal}{Journal of Earth System Science}
\newcommand{\Author}{J. John Savio, V. Yatheesh, et al.}

\newcommand{\AuthorAffil}{
	{\large
		J. John Savio$^{1,2}$
		V. Yatheesh$^{1,*}$
		R. Sheldon$^{1}$
		M. Kallathian$^{1}$
		Pratima Kessarkar$^{1}$}\\
	{\large
		Kuldeep Kumar$^{1}$
		P. Mahesh$^{1}$
		Subhashree Mishra$^{1}$
		Swati Verma$^{1}$
	}
	\\[0.4cm]
	{\small $^1$ CSIR -  National Institute of Oceanography, Dona Paula, Goa -  403 004, India}
	\\
	{\small $^2$ School of Earth, Ocean and Atmospheric Sciences, Goa University, Taleigao Plateau, Goa -  403 206, India}
	\\
	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
}
\newcommand{\DOI}{doi:\href{https://doi.org/10.xxxx/jess/xxxxxx}{10.xxxx/jess/xxxxxx}}
\newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's

\usepackage[left=0.7in,right=0.7in,top=0.9in,bottom=0.8in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8x]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage[round]{natbib}
\hbadness=99999
%%\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=blue,
	pdftitle={\Title},
	pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{caption}
\fancyhf{}
\lhead{
	\fontsize{9pt}{12pt}\selectfont
	\Author{}, 2021, \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\title{\Title}
\author{\AuthorAffil}
\date{
\normalsize
Manuscipt Received - xx June 2021; Revised - xx October 2021; Accepted - 05 November 2021
\\[0.4cm] 
\justifying{
This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review. The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2021. \Title{}, \Journal{},}\ " is available online at: \DOI{}
}}
\maketitle

\begin{abstract}
The Laxmi Basin, which is believed to have been formed by the divergence between India and the Laxmi Ridge, contains a seamount chain consisting of the Raman Seamount, Panikkar Seamount and the Wadia Guyot in its axial region. Some authors considered that these seamounts are underlain by stretched continental crust, while others attributed the genesis of these seamounts to an anomalous episode of volcanism resulting from the interaction of the R\'eunion hotspot with the extinct spreading centre. In absence of any direct evidences to these contradicting views, we carried out a detailed multibeam bathymetry survey over a selected sector of this seamount chain and collected a fresh set of high-resolution bathymetry data. Our analysis of this bathymetry data reveals the presence of six semicircular scarp faces enclosing nearly flat seafloor over the Panikkar Seamount, with their morphology resembling with the shape of volcanic calderas. Based on the presence of these caldera-like features, in conjunction with the constraints of plate tectonic framework of this region, we corroborate the volcanic origin for the seamount chain located in the axial part of the Laxmi Basin.
\\[0.6cm]
\textbf{Keywords:}
Volcanic caldera; Laxmi Basin; Panikkar Seamount; bathymetry; morphology.
\end{abstract}

\section{Introduction}
The deep ocean basin existing between the Laxmi Ridge in the west and the Indian continental margin in the east represents the Laxmi Basin (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}). Although the researchers broadly agree that the Laxmi Basin was formed by divergence, difference in opinion exists about the nature of crust underlying this basin. Some researchers \citep{Naini1982,Kolla1990,Todal1998,Krishna2006,Nemcok2017,Geoffroy2020} consider this basin to have been formed only by continental rifting resulting in thinned continental crust, while others \citep{Biswas1988,Bhattacharya1994a,Talwani1998,Bernard2000,Yatheesh2007,Corfield2010,Eagles2013,Siawal2014,Bhattacharya2015,Misra2015,Ramana2015} consider this basin to have been formed by continental rifting followed by seafloor spreading resulting in the formation of the oceanic crust. The inference on continental origin of the Laxmi Basin is mainly based on the semi-continental crustal thickness and lack of identifiable seafloor spreading type magnetic anomalies, while the oceanic origin is inferred based on the symmetric magnetic anomalies that can be explained in terms of juxtaposed normal and reversely magnetized oceanic crustal blocks, hyperbolic reflection pattern in the multi-channel seismic reflection sections, and the presence of Seaward Dipping Reflectors (SDRs) landward of the Laxmi Ridge and seaward of the western continental slope of India.
The axial part of the Laxmi Basin is characterized by the presence of three isolated seamounts, referred to as the Raman Seamount, Panikkar Seamount and Wadia Guyot \citep{Bhattacharya1994b}, from the north to south (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}). These seamounts, together forming an axial seamount chain in the Laxmi Basin \citep{Bhattacharya1994b}, situates on an ~ 360 km long, NNW-SSE striking ridge buried under the sediments (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}), referred to as the Panikkar Ridge \citep{Gopala_Rao1992}. The supporters of continental origin hypothesis for the formation of the Laxmi Basin interpreted the Panikkar Ridge to\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.85\linewidth]{studyarea-bathy.pdf}
	\caption{
	Topographic map of the northwestern continental margin of India and the adjoining deep oceans basins as depicted by the GEBCO 2021 global terrain model for ocean and land \citep{GEBCO_Compilation_Group2021}, showing the locations of the Panikkar Ridge (shown as thick white line) and the axial seamount chain in the Laxmi Basin. Thin black lines are selected (1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours from GEBCO 2021 data set. The box shown with thick dashed black lines represents the boundary of the tectonic map shown in Figure 2. LXR: Laxmi Ridge; LXB: Laxmi Basin; ABB: Arabian Basin; PKR: Panikkar Ridge; LCP: Laccadive Plateau. R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot
	}
	\label{fig:studyarea}
\end{figure*} represent a structural feature of less altered stretched continental crust \citep{Krishna2006}, or an isolated continental block \citep{Geoffroy2020}. \cite{Krishna2006} further considered that the Raman Seamount, Panikkar Seamount and Wadia Guyot represent the isolated highs of the Panikkar Ridge elevated above the seafloor, implying a continental origin for these seamounts. In contrary to this, the supporters of oceanic crust hypothesis for the formation of the Laxmi Basin inferred that the Panikkar Ridge represents the extinct spreading centre in the Laxmi Basin \citep{Bhattacharya1994a,Bhattacharya1994b}, where two-limbed seafloor spreading initiated at around 67.6 Ma and ceased at ~56.4 Ma, as interpreted from the identified magnetic anomaly sequence C30n-C25r-C30n \citep{Bhattacharya2015,Yatheesh2020}. Further, those studies attributed the genesis of the Raman-Panikkar-Wadia seamount chain located over the Panikkar Ridge to an anomalous episode of volcanism resulting from the interaction of the R\'eunion hotspot with the spreading centre in the Laxmi Basin. These seamounts are considered to have been emplaced at around 62.5 Ma \citep{Bhattacharya2015,Yatheesh2020}, coeval with the emplacement of Ghatkopar-Powai tholeiites on the Indian mainland \citep{Pande2017}. However, any direct evidences from this seamount chain to represent their genesis in terms of volcanic eruptions is still awaited. Towards this, we carried out a multibeam bathymetry survey over a selected sector of this seamount chain to
\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.8\linewidth]{tectonic-framework.pdf}
	\caption{
		Generalized tectonic map of the northwestern continental margin of India and the adjoining deep ocean basins. The blue coloured box represents the study area. Grey coloured thin dotted lines represent the selected (200 m., 1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours. Grey coloured continuous lines represent the inferred magnetic lineations in the Laxmi Basin  \citep{Bhattacharya2015} and the solid red coloured patches in the axial part of the Laxmi Basin represent the extent of the seamount chain \citep{Bhattacharya1994b} consisting of the Raman Seamount (R), Panikkar Seamount (P) and the Wadia Guyot (W). The green-coloured region represents the extent of the Panikkar Ridge (PKR).  Other details are as in Figure \ref{fig:studyarea}.
	}
	\label{fig:studyarea2}
\end{figure*}
understand the detailed seafloor morphology of this anomalous feature. In this paper, we present the preliminary morphotectonic information derived from the analysis of this fresh set of recently acquired high-resolution multibeam bathymetry data.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data and Methodology}
A multidisciplinary scientific expedition was conducted onboard \textit{RV Sindhu Sadhana}, by the CSIR – National Institute of Oceanography, Goa, India, during 28\textsuperscript{th} August to 10\textsuperscript{th} September 2020. As a part of this expedition, multibeam bathymetry data were collected over selected sectors in the axial part of the Laxmi Basin, where the Raman-Panikkar-Wadia seamount chain is located. The multibeam bathymetry data was collected using Teledyne-Atlas multibeam echo sounders, operated at a frequency of 15 kHz. These data were corrected for variation of sound velocity in sea water by collecting sound velocity profiles in real time. The PDS software was used to process the data, first by removing erroneous values and then applying the most suitable qualitative filters. Using this data, a bathymetric grid of 100 m spatial resolution was generated and the bathymetric maps were plotted using the Generic Mapping Tools software \citep{Wessel2019}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
	\centering
	\includegraphics[width=\textwidth]{panikkar-seamount.pdf}
	\caption{
		Colour-coded bathymetric map of the Panikkar Seamount and the adjacent regions, showing (a) the morphology of the seafloor and (b) the interpreted caldera-like features. The thin black lines represent selected (3600 m. and 3650 m.) isobaths. S1, S2 and S3 represent the Segment-1, Segment-2 and Segment-3 of the Panikkar Seamount. The labels C1 through C6 represent the locations of inferred caldera-like features. The thick black circles represent the postulated extent of rims of these inferred calderas as seen from the bathymetry data (continuous semi-circles) and as considered to have buried under the sediments (dotted semi-circles).
	}
	\label{panikkar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminary results and discussion}
We present high-resolution multibeam bathymetry data as a colour-coded two-dimensional (Figures \ref{panikkar}a\&b) and three-dimensional (Figures \ref{calderas}a-c) images over a segment of the Laxmi Basin Seamount chain, i.e., over the Panikkar Seamount and the adjoining regions. The multibeam bathymetric map (Figure \ref{panikkar}a) clearly depicts the presence of three bathymetric highs, together forming an arcuate shape. Among these, the two larger features with major peaks sitting on a single base defined by 3600 m. isobath, represent the Panikkar Seamount discovered by \cite{Bhattacharya1994b}. The third bathymetric high identified in the present study also appears to form a part of this anomalous feature, and therefore, Panikkar Seamount can be considered to consists of three segments. For the ease of reference, in this paper, we refer these segments as Segment-1 (S1), Segment-2 (S2) and Segment-3 (S3) of the Panikkar Seamount, from northwest to southeast, respectively (Figure \ref{panikkar}a). Among these, the Segment-1 (S1) represents the largest feature, whose western side is characterized by a sharp boundary defined by the 3650 m. and 3600 m. isobaths. In the eastern side of this segment, north of 16°09’N, the bathymetric high shows similar sharp drop in the depth as in the case of western limit, however, towards south, this feature shows a relatively gentle topography. Similarly, the Segment-2 (S2) is associated with a sharp boundary in the southwestern side and a relatively gentle topography on its eastern side. However, the bathymetric map of the regions adjacent to these two segments, Segment-1 and Segment-2, clearly depicts the presence of isolated, characteristic semi-circular, scarp faces / embayments with a moderately steep slope that are dipping to a nearly flat seafloor region away from the crest of the seamount, in the southwestern as well as eastern sides of these anomalous bathymetric features (Figure \ref{panikkar}a). Similarly, the Segment-3, which is separated from Segment-2 by a relatively deeper seafloor, is also characterized by the presence of two smaller semi-circular bathymetric features (Figure \ref{panikkar}a). Morphologically, such rim-like features enclosing a region of nearly flat seafloor associated with all the three segments of the Panikkar Ridge are very interesting, since this geometry closely resembles with the shape of volcanic caldera structures associated with the submarine volcanic events. Such volcanic calderas generally form due to the collapse or subsidence into the top of a magma chamber \citep{Cole2005}. \cite{Bijesh2021} has recently reported the presence of an extinct giant volcanic caldera in the Arabian Sea, southwest of the Laccadive Plateau, based on the presence of a nearly elliptical bathymetry high complex, known as the Sagar Kanya Bathymetric High Complex, enclosing a nearly flat seafloor region.
\begin{minipage}{\linewidth}% to keep image and caption on one page
	\vspace{7.5mm} %5mm vertical space
	\makebox[\linewidth]{%        to center the image
		\noindent\includegraphics[width=1.09\linewidth,keepaspectratio]{panikkar-caldera.pdf}}
	\captionof{figure}{ Colour-coded three-dimensional bathymetry maps representing postulated calderas (a) C1 and C2; (b) C3 and C4; and (c) C5 and C6. Other details are as in Figure \ref{panikkar}.}\label{calderas}
	\vspace{4mm} %5mm vertical space
\end{minipage}

From the colour-coded two-dimensional bathymetric image (Figure \ref{panikkar}a, b), we identify six semi-circular scarp faces, labeled as C1, C2, C3, C4, C5 and C6, having diameters 6.7 km., 11.7 km., 2.3 km., 4.5 km., 2.5 km., and 4.0 km., respectively, and present their morphology in three-dimensional perspective (Figures \ref{calderas} a-c). It is important to note that almost all these scarp faces are semi-circular in nature, but theoretically, all the volcanic calderas should be associated with circular rim structures. To examine this, we referred the published literature depicting the morphology of various known volcanic calderas, such as  the Santorini Caldera \citep{Nomikou2012}, Nikko Submarine Volcanic Caldera \citep{Global_Volcanism_Program1990}, the Brothers Seamount Caldera \citep{Stagpoole2016}, Henderson Seamount Caldera \citep{Taylor1980}, and the Sagar Kanya Volcanic Caldera \citep{Bijesh2021}. Interestingly, none of these volcanic calderas are associated with complete circular rim structures all over 360°, as seen in the bathymetry data, and the absence of rim structure at parts of these calderas have been interpreted to represent a morphological configuration of buried rim structure, associated with the asymmetrical subsidence resulted by tilting of the magma chamber \citep{Kennedy2004}. We believe, this explanation reasonably holds good to explain the semi-circular nature of the postulated volcanic calderas adjacent to the Panikkar Seamount; the segments of the rim structure missing from the seafloor image might represent buried rim structure associated with asymmetric subsidence as in the case of the above volcanic calderas and the observed dipping of seafloor containing the rim structure away from the crest of the seamount towards deeper region further support this asymmetric subsidence and tilting of magma chamber.

It may be noted that the inferred caldera-like features are concentrated south of 16° 08’N latitude on the Panikkar Seamount, while the northern part of this seamount is devoid of such prominent features. In the north, the Segment S-1 contains multiple peaks on a single base and the least depth over the largest of these peaks (near 16°13'N) is about 2618 m., which is much higher from the surrounding seafloor than the other two segments, suggesting multiple phases of volcanism over the Segment S-1 of the Panikkar Seamount. As in the case of region south of 16° 08’N latitude, volcanic caldera-like features might have been formed in this norther region also, however, the later phases of volcanism occurred in the northernmost part of the Panikkar Seamount might have obliterated the morphological features representing caldera-like feature formed as a result of the early phases of volcanism.   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary and Conclusion}

The updated bathymetric map of the Panikkar Seamount and the adjacent regions depicts the presence of three segments of bathymetric highs, of which two larger features (Segment-1 and Segment-2) are sitting on a single base defined by 3600 m. isobath and the third one (Segment-3) is separated from Segment-2 by a relatively deeper seafloor. These regions are associated with six characteristic semi-circular scarp faces enclosing nearly flat seafloor, deepening away from the crest of the major peak of the bathymetric highs of all the segments. We interpret these features to represent volcanic calderas associated with the submarine volcanic events. Considering the presence of these volcanic calderas over the Panikkar Seamount and the adjacent regions, in conjunction with the published information on the presence of an extinct spreading centre under the influence of R\'eunion hotspot, we attribute the genesis of seamount chain in the Laxmi Basin to the R\'eunion hotspot volcanism during the waning stage of seafloor spreading in the Laxmi Basin. Therefore, based on the analysis of our recently collected multibeam bathymetry data, we corroborate volcanic origin for the seamount chain in the axial part of the Laxmi Basin in contrary to the concept of underlying continental crust. However, a detailed geochronological investigation by collecting the rock samples from this region needs to be carried out for providing age constraint for this inferred episode of volcanism responsible for the formation of the Panikkar Seamount.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}

The authors are grateful to Prof. Sunil Kumar Singh, Director, CSIR-National Institute of Oceanography (CSIR-NIO), Goa, India, for providing ship time and granting permission to publish this work. This study forms a part of PhD work of JJS at Goa University. JJS thank Council of Scientific \& Industrial Research (CSIR), New Delhi, India, for the financial support under Junior Research Fellowship (Grant No. 31/026(0321)/2019-EMR-I). The cooperation and support received from the Captain and his operational team onboard \textit{RV Sindhu Sadhana} during the expedition SSD-073 are acknowledged. We thank Dr. V.J. Loveson, Head, Geological Oceanography Division for useful discussions, and Mr. S. Gautham for the help extended in processing the bathymetry data. We are grateful to an anonymous reviewer for his constructive review and valuable suggestions that improved our manuscript, and to Dr. N.V. Chalapathi Rao for editorial handling. All figures were drafted with the GMT software  \citep{Wessel2019}. This is NIO contribution xxxx.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Author statement}

J. John Savio: Conceptualized the idea, acquisition and processing of the data, preparation of first draft of the manuscript; V. Yatheesh: Conceptualized the idea, interpretation, correction of the manuscript; R. Sheldon: Data acquisition and quality check; M. Kallathian: Data acquisition and quality check; Pratima Kessarkar: Data acquisition; Kuldeep Kumar: Data acquisition; P. Mahesh: Data acquisition; Subhashree Mishra: Data acquisition; Swati Verma: Data acquisition. All authors contributed to the correction and finalization of the manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{gji-doi-link}
\bibliography{references}
\appendix

\end{document}

### 2021-12-20 manuscript/manuscript.tex
Updated manuscript
Update manuscript.tex

--- 2021-12-02 manuscript.tex
@@
 	{\large
-		J. John Savio$^{1,2}$
-		V. Yatheesh$^{1,*}$
-		R. Sheldon$^{1}$
-		M. Kallathian$^{1}$
-		Pratima Kessarkar$^{1}$}\\
+		J. John Savio$^{1,2}$,
+		V. Yatheesh$^{1,*}$,
+		R. Sheldon$^{1}$,
+		M. Kallathian$^{1}$,
+		Pratima Kessarkar$^{1}$},\\
 	{\large
-		Kuldeep Kumar$^{1}$
-		P. Mahesh$^{1}$
-		Subhashree Mishra$^{1}$
-		Swati Verma$^{1}$
+		Kuldeep Kumar$^{1}$,
+		P. Mahesh$^{1}$,
+		Subhashree Mishra$^{1}$,
+		and Swati Verma$^{1}$
 	}
@@
 }
-\newcommand{\DOI}{doi:\href{https://doi.org/10.xxxx/jess/xxxxxx}{10.xxxx/jess/xxxxxx}}
+\newcommand{\DOI}{\href{https://doi.org/10.xxxx/jess/xxxxxx}{https://doi.org/xxxxxx}}
 \newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's
@@
 \setlength{\columnsep}{2\columnsep}
-\usepackage[utf8x]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{timet}
@@
 	\fontsize{9pt}{12pt}\selectfont
-	\Author{}, 2021, \DOI{}
+	\Author{}, Accepeted article, \textit{\Journal{}}
 }
@@
 \normalsize
-Manuscipt Received - xx June 2021; Revised - xx October 2021; Accepted - 05 November 2021
+Manuscipt Received - 12 May 2021; Revised - October 2021; Accepted - 05 November 2021
 \\[0.4cm] 
@@
 This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review.
-The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2021.
+The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2022.
 \Title{}, \Journal{},}\ " is available online at: \DOI{}
@@
 All figures were drafted with the GMT software  \citep{Wessel2019}.
-This is NIO contribution xxxx.
+This is NIO contribution 6836.
 

### 2021-12-27 manuscript/manuscript.tex
Update manuscript.tex

@@
 
-\newcommand{\Title}{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}
+\newcommand{\Title}{\textbf{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}}
 \newcommand{\Journal}{Journal of Earth System Science}
@@
 }
-\newcommand{\DOI}{\href{https://doi.org/10.xxxx/jess/xxxxxx}{https://doi.org/xxxxxx}}
+\newcommand{\DOI}{\href{https://doi.org/10.1007/s12040-021-01797-7}{10.1007/s12040-021-01797-7}}
 \newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's
@@
 	\fontsize{9pt}{12pt}\selectfont
-	\Author{}, Accepeted article, \textit{\Journal{}}
+	\Author{}, \DOI{}
 }
@@
 \normalsize
-Manuscipt Received - 12 May 2021; Revised - October 2021; Accepted - 05 November 2021
+MS received - 12 May 2021; revised - 27 October 2021; accepted - 05 November 2021
 \\[0.4cm] 
@@
 	\caption{
-	Topographic map of the northwestern continental margin of India and the adjoining deep oceans basins as depicted by the GEBCO 2021 global terrain model for ocean and land \citep{GEBCO_Compilation_Group2021}, showing the locations of the Panikkar Ridge (shown as thick white line) and the axial seamount chain in the Laxmi Basin.
+\textsl{	Topographic map of the northwestern continental margin of India and the adjoining deep oceans basins as depicted by the GEBCO 2021 global terrain model for ocean and land \citep{GEBCO_Compilation_Group2021}, showing the locations of the Panikkar Ridge (shown as thick white line) and the axial seamount chain in the Laxmi Basin.
 Thin black lines are selected (1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours from GEBCO 2021 data set.
-The box shown with thick dashed black lines represents the boundary of the tectonic map shown in Figure 2.
+The box shown with thick dashed black lines represents the boundary of the tectonic map shown in Figure \ref{fig:studyarea2}.
 LXR: Laxmi Ridge; LXB: Laxmi Basin; ABB: Arabian Basin; PKR: Panikkar Ridge; LCP: Laccadive Plateau.
-R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot
+R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot}
 	}
@@
 	\caption{
-		Generalized tectonic map of the northwestern continental margin of India and the adjoining deep ocean basins.
+	\textsl{	Generalized tectonic map of the northwestern continental margin of India and the adjoining deep ocean basins.
 The blue coloured box represents the study area.
@@
 The green-coloured region represents the extent of the Panikkar Ridge (PKR).
-Other details are as in Figure \ref{fig:studyarea}.
+Other details are as in Figure \ref{fig:studyarea}.}
 	}
@@
 	\caption{
-		Colour-coded bathymetric map of the Panikkar Seamount and the adjacent regions, showing (a) the morphology of the seafloor and (b) the interpreted caldera-like features.
+		\textsl{Colour-coded bathymetric map of the Panikkar Seamount and the adjacent regions, showing (a) the morphology of the seafloor and (b) the interpreted caldera-like features.
 The thin black lines represent selected (3600 m.
@@
 The labels C1 through C6 represent the locations of inferred caldera-like features.
-The thick black circles represent the postulated extent of rims of these inferred calderas as seen from the bathymetry data (continuous semi-circles) and as considered to have buried under the sediments (dotted semi-circles).
+The thick black circles represent the postulated extent of rims of these inferred calderas as seen from the bathymetry data (continuous semi-circles) and as considered to have buried under the sediments (dotted semi-circles).}
 	}
@@
 		\noindent\includegraphics[width=1.09\linewidth,keepaspectratio]{panikkar-caldera.pdf}}
-	\captionof{figure}{ Colour-coded three-dimensional bathymetry maps representing postulated calderas (a) C1 and C2; (b) C3 and C4; and (c) C5 and C6.
-Other details are as in Figure \ref{panikkar}.}\label{calderas}
+	\captionof{figure}{ \textsl{Colour-coded three-dimensional bathymetry maps representing postulated calderas (a) C1 and C2; (b) C3 and C4; and (c) C5 and C6.
+Other details are as in Figure \ref{panikkar}.}}
+	\label{calderas}
 	\vspace{4mm} %5mm vertical space

### 2022-09-27 manuscript/manuscript.tex
Updated Manuscript
Update manuscript.tex

@@
 \documentclass[twocolumn]{article}
-
 \newcommand{\Title}{\textbf{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}}
 \newcommand{\Journal}{Journal of Earth System Science}
-\newcommand{\Author}{J. John Savio, V. Yatheesh, et al.}
+\newcommand{\Author}{J. John Savio, V. Yatheesh et al. (2022)}
 
@@
 	\\
-	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
+	{\small $^*$ Corresponding author e-mail:\hspace{2mm} yatheesh@nio.org \hspace{2mm} yatheeshv@gmail.com}
 }
@@
 	pdfauthor={\Author},
+	pdfpagemode=UseNone
 }
@@
 \normalsize
-MS received - 12 May 2021; revised - 27 October 2021; accepted - 05 November 2021
+Manuscript received - 12 May 2021; Manuscript revised - 27 October 2021; \\ Accepted - 05 November 2021; Final version published - 02 February 2022
 \\[0.4cm] 
@@
 The inference on continental origin of the Laxmi Basin is mainly based on the semi-continental crustal thickness and lack of identifiable seafloor spreading type magnetic anomalies, while the oceanic origin is inferred based on the symmetric magnetic anomalies that can be explained in terms of juxtaposed normal and reversely magnetized oceanic crustal blocks, hyperbolic reflection pattern in the multi-channel seismic reflection sections, and the presence of Seaward Dipping Reflectors (SDRs) landward of the Laxmi Ridge and seaward of the western continental slope of India.
-The axial part of the Laxmi Basin is characterized by the presence of three isolated seamounts, referred to as the Raman Seamount, Panikkar Seamount and Wadia Guyot \citep{Bhattacharya1994b}, from the north to south (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}).
-These seamounts, together forming an axial seamount chain in the Laxmi Basin \citep{Bhattacharya1994b}, situates on an ~ 360 km long, NNW-SSE striking ridge buried under the sediments (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}), referred to as the Panikkar Ridge \citep{Gopala_Rao1992}.
-The supporters of continental origin hypothesis for the formation of the Laxmi Basin interpreted the Panikkar Ridge to\begin{figure*}[!htb]
+\begin{figure*}[!htb]
 	\centering
@@
 LXR: Laxmi Ridge; LXB: Laxmi Basin; ABB: Arabian Basin; PKR: Panikkar Ridge; LCP: Laccadive Plateau.
-R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot}
+R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot.}
 	}
 	\label{fig:studyarea}
-\end{figure*} represent a structural feature of less altered stretched continental crust \citep{Krishna2006}, or an isolated continental block \citep{Geoffroy2020}.
+\end{figure*} 
+The axial part of the Laxmi Basin is characterized by the presence of three isolated seamounts, referred to as the Raman Seamount, Panikkar Seamount and Wadia Guyot \citep{Bhattacharya1994b}, from the north to south (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}).
+These seamounts, together forming an axial seamount chain in the Laxmi Basin \citep{Bhattacharya1994b}, situates on an {$\sim$} 360 km long, NNW-SSE striking ridge buried under the sediments (Figures \ref{fig:studyarea} \& \ref{fig:studyarea2}), referred to as the Panikkar Ridge \citep{Gopala_Rao1992}.
+The supporters of continental origin hypothesis for the formation of the Laxmi Basin interpreted the Panikkar Ridge to represent a structural feature of less altered stretched continental crust \citep{Krishna2006}, or an isolated continental block \citep{Geoffroy2020}.
 \cite{Krishna2006} further considered that the Raman Seamount, Panikkar Seamount and Wadia Guyot represent the isolated highs of the Panikkar Ridge elevated above the seafloor, implying a continental origin for these seamounts.
-In contrary to this, the supporters of oceanic crust hypothesis for the formation of the Laxmi Basin inferred that the Panikkar Ridge represents the extinct spreading centre in the Laxmi Basin \citep{Bhattacharya1994a,Bhattacharya1994b}, where two-limbed seafloor spreading initiated at around 67.6 Ma and ceased at ~56.4 Ma, as interpreted from the identified magnetic anomaly sequence C30n-C25r-C30n \citep{Bhattacharya2015,Yatheesh2020}.
-Further, those studies attributed the genesis of the Raman-Panikkar-Wadia seamount chain located over the Panikkar Ridge to an anomalous episode of volcanism resulting from the interaction of the R\'eunion hotspot with the spreading centre in the Laxmi Basin.
-These seamounts are considered to have been emplaced at around 62.5 Ma \citep{Bhattacharya2015,Yatheesh2020}, coeval with the emplacement of Ghatkopar-Powai tholeiites on the Indian mainland \citep{Pande2017}.
-However, any direct evidences from this seamount chain to represent their genesis in terms of volcanic eruptions is still awaited.
-Towards this, we carried out a multibeam bathymetry survey over a selected sector of this seamount chain to
 \begin{figure*}[!htb]
@@
 \end{figure*}
-understand the detailed seafloor morphology of this anomalous feature.
+In contrary to this, the supporters of oceanic crust hypothesis for the formation of the Laxmi Basin inferred that the Panikkar Ridge represents the extinct spreading centre in the Laxmi Basin \citep{Bhattacharya1994a,Bhattacharya1994b}, where two-limbed seafloor spreading initiated at around 67.6 Ma and ceased at ~56.4 Ma, as interpreted from the identified magnetic anomaly sequence C30n-C25r-C30n \citep{Bhattacharya2015,Yatheesh2020}.
+Further, those studies attributed the genesis of the Raman-Panikkar-Wadia seamount chain located over the Panikkar Ridge to an anomalous episode of volcanism resulting from the interaction of the R\'eunion hotspot with the spreading centre in the Laxmi Basin.
+These seamounts are considered to have been emplaced at around 62.5 Ma \citep{Bhattacharya2015,Yatheesh2020}, coeval with the emplacement of Ghatkopar-Powai tholeiites on the Indian mainland \citep{Pande2017}.
+However, any direct evidences from this seamount chain to represent their genesis in terms of volcanic eruptions is still awaited.
+Towards this, we carried out a multibeam bathymetry survey over a selected sector of this seamount chain tounderstand the detailed seafloor morphology of this anomalous feature.
 In this paper, we present the preliminary morphotectonic information derived from the analysis of this fresh set of recently acquired high-resolution multibeam bathymetry data.
@@
 Morphologically, such rim-like features enclosing a region of nearly flat seafloor associated with all the three segments of the Panikkar Ridge are very interesting, since this geometry closely resembles with the shape of volcanic caldera structures associated with the submarine volcanic events.
-Such volcanic calderas generally form due to the collapse or subsidence into the top of a magma chamber \citep{Cole2005}.
-\cite{Bijesh2021} has recently reported the presence of an extinct giant volcanic caldera in the Arabian Sea, southwest of the Laccadive Plateau, based on the presence of a nearly elliptical bathymetry high complex, known as the Sagar Kanya Bathymetric High Complex, enclosing a nearly flat seafloor region.
-\begin{minipage}{\linewidth}% to keep image and caption on one page
+Such volcanic calderas generally form due to the collapse or subsidence into the \begin{minipage}{\linewidth}% to keep image and caption on one page
 	\vspace{7.5mm} %5mm vertical space
@@
 \end{minipage}
+top of a magma chamber \citep{Cole2005}.
+\cite{Bijesh2021} has recently reported the presence of an extinct giant volcanic caldera in the Arabian Sea, southwest of the Laccadive Plateau, based on the presence of a nearly elliptical bathymetry high complex, known as the Sagar Kanya Bathymetric High Complex, enclosing a nearly flat seafloor region.
 
@@
 It may be noted that the inferred caldera-like features are concentrated south of 16° 08’N latitude on the Panikkar Seamount, while the northern part of this seamount is devoid of such prominent features.
-In the north, the Segment S-1 contains multiple peaks on a single base and the least depth over the largest of these peaks (near 16°13'N) is about 2618 m., which is much higher from the surrounding seafloor than the other two segments, suggesting multiple phases of volcanism over the Segment S-1 of the Panikkar Seamount.
-As in the case of region south of 16° 08’N latitude, volcanic caldera-like features might have been formed in this norther region also, however, the later phases of volcanism occurred in the northernmost part of the Panikkar Seamount might have obliterated the morphological features representing caldera-like feature formed as a result of the early phases of volcanism.
+In the north, the Segment S1 contains multiple peaks on a single base and the least depth over the largest of these peaks (near 16°13'N) is about 2618 m., which is much higher from the surrounding seafloor than the other two segments, suggesting multiple phases of volcanism over the Segment S1 of the Panikkar Seamount.
+As in the case of region south of 16° 08’N latitude, volcanic caldera-like features might have been formed in this norther region also, however, the later phases of volcanism occurred in the northernmost part of the Panikkar Seamount might have obliterated the morphological features formed as a result of the early phases of volcanism.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
